\documentclass{article}
\usepackage{url}
\usepackage{graphicx}
\begin{document}
\title{Informe de Tarea 2 - Juego Skynet}
\author{Francisco Ar\'evalo\\
  \texttt{francisco.arevalod@alumnos.usm.cl}\\
  \texttt{http://github.com/farevalod/fisw-tarea2}\\
  \vspace{10mm}
  Departamento de Inform\'atica\\
  Universidad T\'ecnica Federico Santa Mar\'ia\\
  Santiago, Chile}
\date{\today}
\maketitle
\tableofcontents
\section{Goals and Objectives}
\subsection{Business}
\paragraph{\textbf{Goal}: Promote exercise among users}
\subparagraph{Develop an active Alternate Reality Game}
Players must disable all robots to survive. They must explore the game area to find robots and items.
\subparagraph{It should be very easy to adopt}
Users should be able to start playing right away. No need for training.
\subsection{Project}
\paragraph{\textbf{Goal}: Active interfaces}
Active interfaces are designed to be used while playing, and enable the user to focus on the game instead of bothering with buttons and menus.\\
\textit{Pinch to interact with robot, slide to display more info, use GPS to update position.}
\paragraph{\textbf{Goal}: Study robot performance and stats}
Track robot type, HP, speed, attack and armour types. Study performance and behaviour (fight-or-flight response) for different parameters.
\subsection{System}
\paragraph{\textbf{Goal}: Tracking}
Track players, scores, robots and items (guns, ammo). Players get scored for games played, robots disabled, remaining HP and collected items. Score can be traded for perks before a match. 
\subparagraph{Enable users to play solo or team-up}
Players will be ranked individually and by teams.
\paragraph{\textbf{Goal}: Manageable}
\subparagraph{Enable GameMasters to setup game parameters}
Game map zone, number of players, robots, and items can be set up by a GameMaster. He can customize these options choosing the map polygon, robot types, item type, amount and positioning.
\section{Requirements}
\subsection{Functional}
\paragraph{Robots}
A player can disable a robot using available items or run away to another area. Robots can move around, and have different types of armour.
\paragraph{Teams}
Users can maintain their team status. Teams are ranked on the team leaderboard.
\paragraph{Explore}
Users explore the game polygon. They discover robots and items.
\paragraph{Items}
Items have position, type and number. They can be discovered by players. They can be used to disable robots.
\paragraph{Setup}
GM must setup game options.
\paragraph{Views}
\subparagraph{Map}
Shows discovered Robots, players nearby
\subparagraph{Augmented Reality}
Find Robots and items
\subsection{Non-Functional}
\paragraph{Endgame}
\subparagraph{GM Ends game}
\subparagraph{Humans win}
All robots are disabled.
\subparagraph{Robots win}
Submission or elimination.
\paragraph{Logs/Score}
Robots disabled/Players eliminated, timestamps, distance travelled, items used.
\paragraph{Top Player/Team}
Group players by teams, show top player and team ranking.
\section{Use Case Diagram}
\subsection{Actors}
\paragraph{Player}
\paragraph{Robot}
\paragraph{Item}
\paragraph{Game-Master}
\paragraph{Team}
\subsection{Cases}
\textbf{Player} discovers \textbf{Robot}\\
\textbf{Player} discovers \textbf{Item}\\
\textbf{Player} uses \textbf{Item}\\
\textbf{Robot} is disabled by \textbf{Item}\\
\textbf{Robot} attacks \textbf{Player}\\
\textbf{Player} manages \textbf{Team}\\
\textbf{Game-Master} configures\\
\subsection{Relationship between Cases}
A Game-Master sets up a new game.\\
A player discovers a robot and disables it using a previously-found item.\\
The game finishes because all robots are disabled.\\
\end{document}
