\documentclass{beamer}
\usetheme{Berlin}
\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{alltt}
\usepackage[spanish]{babel}
\title{Informe de Tarea 2 - Juego Skynet}
\author{Francisco Ar\'evalo\\
  \texttt{francisco.arevalod@alumnos.usm.cl}\\
  \texttt{http://github.com/farevalod/fisw-tarea2}\\
  \vspace{10mm}
  Departamento de Inform\'atica\\
  Universidad T\'ecnica Federico Santa Mar\'ia\\
  Santiago, Chile}
\date{\today}
\begin{document}
\maketitle
\tableofcontents
\section{Goals and Objectives}
\begin{frame}
\frametitle{Goals and Objectives}
\subsection{ARG}
Develop an active Alternate Reality Game
\begin{itemize}
	\item \textbf{Goal}: Promote exercise among users
	\item Players must disable all robots to survive. 
	\item They must explore the game area to find robots and items.
\end{itemize}
\subsection{Ease-of-use}
It should be very easy to adopt
\begin{itemize}
	\item \textbf{Goal}: Active interfaces
	\item Users should be able to start playing right away. 
	\item No need for training.
	\item Active interfaces are designed to be used while playing instead of bothering with buttons and menus.
\end{itemize}
\subsection{Tracking}
It should track everything
\begin{itemize}
	\item \textbf{Goal}: Study robot performance and stats
	\item Track robot type, performance and fight-or-flight response.
	\item Track players, scores, items and perks.
\end{itemize}
\end{frame}
\section{Requirements}
\subsection{Functional}
\begin{frame}
\frametitle{Functional}
\begin{itemize}
	\item Robots
	\item Teams
	\item Explore
	\item Items
	\item Setup
	\item Views
	\item Map
	\item Augmented Reality
\end{itemize}
\end{frame}
\subsection{Non-Functional}
\begin{frame}
\frametitle{Non-Functional}
\begin{itemize}
	\item Endgame
	\item Logs/Score
 	\item Top Player/Team
\end{itemize}
\end{frame}
\section{Use Case Diagram}
\subsection{Actors}
\begin{frame}
	\begin{itemize}
	\item Player
	\item Robot
	\item Item
	\item Game-Master
	\item Team
\end{itemize}
\end{frame}
\subsection{Cases}
\begin{frame}
\textbf{Player} discovers \textbf{Robot}\\
\textbf{Player} discovers \textbf{Item}\\
\textbf{Player} uses \textbf{Item}\\
\textbf{Robot} is disabled by \textbf{Item}\\
\textbf{Robot} attacks \textbf{Player}\\
\textbf{Player} manages \textbf{Team}\\
\textbf{Game-Master} configures\\
\subsection{Relationship between Cases}
\begin{itemize}
	\item A Game-Master sets up a new game.
	\item A player discovers a robot and disables it using a previously-found item.
	\item The game finishes because all robots are disabled.
\end{itemize}
\end{frame}
\end{document}
